Sampling-Based Motion Planning for Tracking Evolution of Dynamic Tunnels in Molecular Dynamics Simulations

### 2017-10-31 paper.tex
cont, img caption

Besides the exploration of the void space, it is necessary to detect the exit points as well.
The exit points are configurations from $\CG^i$, i.e., they are collision-free at the radius $\gprobe$ and they define the end of the tunnel.
The detection of the exit points requires that the tree exits the protein.
A premature exit from the protein may lead to quick filling of the outer part of the protein and eventually even to entering the protein from outside. 
Such an exploration would lead to the detection of a smaller number of tunnels.
An example as depicted in Fig.~\ref{fig::blocking1}.

@@

\begin{figure}
\centering
{
\renewcommand{\tabcolsep}{1pt}
\begin{tabular}{cccc}
\includegraphics[width=0.24\textwidth]{fig/blockingb1} &
\includegraphics[width=0.24\textwidth]{fig/blockingb2} & 
\includegraphics[width=0.24\textwidth]{fig/blockingb3} & 
\includegraphics[width=0.24\textwidth]{fig/blockingb4} \\
a & b & c & d \\
\end{tabular}  
}
\caption{\label{fig::blocking1}
    Example of the tree growth without the blocking spheres. 
    The initial configuration $\qinit$ (active site) is represented by the black circle.
    The tree starts to grow inside the protein (a) but it can grow outside as well (b).
    In region denoted by A, the tree grows back to the protein (c).
    Finally, two tunnels are detected (with the exit points $P_1$ and $P_2$), but no tunnel is found in the region $A$ (d).
}
\end{figure}

@@

One tunnel is defined by an exit point and by an active site.
A static tunnels is contained completely in one frame, therefore the path from $p \in P^i$ to $\qinit \in \CF^i$ in the graph
$G$ describes it.
Dynamic tunnels have active site and exit point in different frame, so to reconsruct them,
a path from $p \in P^i$ the first reachable $\qinit \in \CF^j, j < i$ has to be searched in the grapg $G$.
%If both these nodes are connected to the same component of the graph, they define a static tunnel.
%Such a tunnel can be reconstructed by finding a path between these two nodes in the graph.
%If there does not exist any path between the exit point $p \in P^i$ (exit point at frame $i$) and the active site $\qinit^i$ in the same frame, the dynamic tunnel has to start from a different active site (in one of the previous frames).
%A path from $p$ to the first active site reachable in the graph (measured by the number of edges) describes the dynamic tunnel.
An example is depicted in Fig.~\ref{fig::components}.

@@

\begin{table}
\centering
\caption{\label{tab::dyn} The number of frames with detected dynamic tunnels. 
    %The number of frames with static tunnels, detected by CAVER 3.0.
}
\begin{tabular}{ccccc}
\toprule
  \multirow{2}{*}{ Proposed method}   &  \multicolumn{2}{c}{ Static tunnels}   \\
                                     &  {\bf Exists} & {\bf Not exists} \\
\midrule                                     
{\bf End of tunnel/cavity}           & 1,324/661 & 1,027/725  \\
{\bf Static tunnel}                  & 3,118     &  0   \\
{\bf No tunnel}                      & 669      & 1,833    \\ 
\bottomrule                                 
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{fig/caver3450-3700}
\caption{\label{fig::caver34} {\textcolor{red}{TODO}}
}
\end{figure}

>>>>

Besides the exploration of the void space, it is necessary to detect the exit points as well.
The exit points are configurations from $\CG^i$, i.e., they are collision-free at the radius $\gprobe$ and they define the end of the tunnel.
The detection of the exit points requires that the tree exits the protein.
A premature exit from the protein may lead to quick filling of the outer part of the protein and eventually even to entering the protein from outside. 
Such an exploration would lead to the detection of a smaller number of tunnels.
The example is depicted in Fig.~\ref{fig::blocking1}.

@@

\begin{figure}
\centering
{
\renewcommand{\tabcolsep}{1pt}
\begin{tabular}{cccc}
\includegraphics[width=0.24\textwidth]{fig/blockingb1} &
\includegraphics[width=0.24\textwidth]{fig/blockingb2} & 
\includegraphics[width=0.24\textwidth]{fig/blockingb3} & 
\includegraphics[width=0.24\textwidth]{fig/blockingb4} \\
a & b & c & d \\
\end{tabular}  
}
\caption{\label{fig::blocking1}
    Example of the tree growth without the blocking spheres. 
    The initial configuration $\qinit$ (active site) is represented by the black circle.
    The tree starts to grow inside the protein (a) but it can grow outside as well (b).
    In region denoted by A, the tree grows back to the protein (c).
    Finally, two tunnels are detected (with the exit points $P_1$ and $P_2$), but any tunnel is found in the region $A$ (d).
}
\end{figure}

@@

One tunnel is defined by an exit point and by an active site.
If both these nodes are connected to the same component of the graph, they define a static tunnel.
Such a tunnel can be reconstructed simply by finding a path between these two nodes in the graph.
If there does not exist any path between the exit point $p \in P^i$ (exit point at frame $i$) and the active site $\qinit^i$ in the same frame, the dynamic tunnel has to start from a different active site (in one of the previous frames).
A path from $p$ to the first active site reachable in the graph (measured by the number of edges) describes the dynamic tunnel.
An example is depicted in Fig.~\ref{fig::components}.

@@

\begin{table}
\centering
\caption{\label{tab::dyn} The number of frames with detected dynamic tunnels. The number of frames
    with static tunnels, detected by CAVER 3.0.
}
\begin{tabular}{ccccc}
\toprule
  \multirow{2}{*}{ Dynamic tunnel}   &  \multicolumn{2}{c}{ Static tunnels}   \\
                                     &  {\bf Exists} & {\bf Not exists} \\
\midrule                                     
{\bf End of tunnel/cavity}           & 1,324/661 & 1,027/725  \\
{\bf Static tunnel}                  & 3,118     &  0   \\
{\bf No tunnel}                      & 669      & 1,833    \\ 
\bottomrule                                 
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{fig/caver3450-3700_colored}
\caption{\label{fig::caver34}
Visualization of tunnels detected using our method (RRT) in comparison to tunnels detected by CAVER.
Both static tunnels detected by CAVER and by our method are depicted in gray.
Then, colored bars show snapshots where a dynamic tunnel was detected by our algorithm.
The dynamic tunnel bars are colored according to the order in which a snapshot occurs in the dynamic tunnel.
It is visible that our method is able to extract many additional information about the void space than traditional static tunnels computed by CAVER.
}
\end{figure}
